EGALITARIAN ASPECTS OF SCALE-FREE NETWORKS

### 2017-08-24 article/article.tex
incorporadas contribs da marilia

In summary, the constant exaltation of the hubs in current
complex networks literature seems to be related to the
fact that the field is still incipient.
A psychologist might also add that it is related to
delusions of grandeur which affect a great fraction of
our society and thus leaks into the scientific tradition.
A social scientist might add that there is a constant
pressure performed by the more powerful and rich groups
to legitimate themselves and the inequality as a natural tendency.
Anyway, there is an evident consonance between the
constant ennoblement of the hubs, the stress on the association
of scale-free networks and inequality,
and our observation that these associations should be
considered with parsimony.

@@

@@

@@

>>>>

In summary, the constant exaltation of the hubs in current
complex networks literature seems to be related to the
fact that the field is still incipient.
A psychologist might also add that it is related to
grandiose delusions which affect a great fraction of
our society and thus leaks into the scientific tradition~\citep{grandiose}.
A social scientist might add that there is a constant
pressure performed by the more powerful and rich groups
to legitimate themselves and the inequality as a natural tendency~\citep{socialB,marcuse}.
An anthropologist might mention societies where the inequality 
is symbolized in rituals as something to be avoided
and extreme cases in which the existence of leaders is denied~\citep{clastres}.
It is also appropriate to remember the notes of~\cite{heisenberg}
about nature, physics and human social power.
Anyway, there is an evident consonance between the
constant ennoblement of the hubs, the stress on the association
of scale-free networks and inequality,
and our observation that these associations should be
considered with parsimony.

@@

\bibitem[Bencze \& Carter, 2005]{socialB}
Bencze, J. L., \& Carter, L. (2015). Capitalists’ Profitable Virtual Worlds: Roles for Science and Science Education. In International Handbook of Semiotics(pp. 1197-1212). Springer Netherlands.

\bibitem[Clastres, 1987]{clastres}
Clastres, P. (1987). Society against the state: essays in political anthropology.

@@

\bibitem[Heisenberg, 1958]{heisenberg}
Heisenberg, W. (1958). The representation of nature in contemporary physics. Daedalus, 87(3), 95-108.

\bibitem[Marcuse, 1967]{marcuse}
Marcuse, H. (1967). The responsibility of science. In The Responsibility of Power (pp. 439-444). Palgrave Macmillan UK.

@@

\bibitem[Smith et al., 2005]{grandiose}
Smith, N., Freeman, D., \& Kuipers, E. (2005). Grandiose delusions: an experimental investigation of the delusion as defense. The Journal of nervous and mental disease, 193(7), 480-487.
